---
title: "patreco-week-5"
author: "wildhtob"
date: "28 5 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r libraries}

library(readr)
library(sf)
library(terra)
library(dplyr)
library(lubridate)
library(ggplot2)
library(tmap)

```

## Import Data

```{r import data}

wildschwein_BE <- read_delim("Data/wildschwein_BE_2056.csv",",") %>%
  st_as_sf(coords = c("E", "N"), crs = 2056, remove = FALSE)

```

## Task 1: Import and visualize spatial data

```{r import spatial data}

fields <- read_sf("Data/Feldaufnahmen_Fanel.gpkg")

ggplot(fields, aes(fill = Frucht)) +
  geom_sf() +
  coord_sf(datum = 2056)

fields

```

Geometry type: Polygon
Data types of cols: FieldID = dbl, Frucht = chr, geom = Polygon [m]
CRS: CH1903+ / LV95


## Task 2: Annotate trajectories from vector data

Filter wildboard data to the months of May to June

```{r filter wildboar data}

wildschwein_BE

wildschwein_filter <- wildschwein_BE %>% 
  mutate(month = month(DatetimeUTC)) %>% 
  filter(month == 5 | month == 6)

```

Overlay the filtered dataset with field data to verify spatial overlap

```{r overlay wildboar with field data}

ggplot() +
  geom_sf(data = fields, aes(fill = Frucht)) +
  geom_point(data = wildschwein_filter, aes(E, N, colour = TierID)) +
  coord_sf(datum = 2056)

```

Create spatial join between wildboar data and field data

```{r spatial join}

wildschwein_join <- st_join(x = wildschwein_filter, y = fields)

```

## Task 3: Explore annotated trajectories

```{r explore trajectories}

wildschwein_sum <- wildschwein_join %>% 
  st_drop_geometry() %>%
  mutate(hour = hour(DatetimeUTC)) %>% 
  group_by(TierName, Frucht, hour) %>% 
  summarise(n = n()) %>%
  group_by(TierName, hour) %>% # regroup by animal and hour to calculate relative sums 
  mutate(n_tot = sum(n),
         sum_rel = n/n_tot)

# Bar charts
ggplot(wildschwein_sum, aes(hour, sum_rel, fill = Frucht)) +
  geom_col() +
  facet_wrap(~ TierName) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Time (rounded to the nearest hour)", y = "Percentage")

# Polar chart
ggplot(wildschwein_sum, aes(hour, sum_rel, fill = Frucht)) +
  geom_col() +
  facet_wrap(~ TierName) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Time (rounded to the nearest hour)", y = "Percentage") +
  coord_polar (start = -0.1)


```

## Task 4: Import ans visualize vegetation index (raster data)

Visualizing raster data using tmap

```{r vegetation index}

vegetation <- terra::rast("data/vegetationshoehe_LFI.tif")
vegetation
plot(vegetation)

  tm_shape(vegetation) +
    tm_raster(palette = "viridis") +
    tm_layout(legend.outside = TRUE)
  
```

## Task 5: Annotate trajectories from raster data

```{r annotate raster data}
wildschwein_coords <- st_coordinates(wildschwein_filter)
vegetation_raster <- extract(vegetation, wildschwein_coords)
wildschwein_raster <- bind_cols(wildschwein_filter, vegetation_raster)

wildschwein_sum2 <- wildschwein_raster %>% 
  st_drop_geometry() %>%
  mutate(hour = hour(DatetimeUTC)) %>% 
  group_by(TierName, vegetationshoehe_LFI, hour) %>% 
  summarise(n = n()) %>%
  group_by(TierName, hour) %>% # regroup by animal and hour to calculate relative sums 
  mutate(n_tot = sum(n),
         sum_rel = n/n_tot)
```

Visualize vegetation height by animal and hour

```{r visualise raster data}

# Bar charts
ggplot(wildschwein_sum2, aes(hour, sum_rel, fill = vegetationshoehe_LFI)) +
  geom_col() +
  facet_wrap(~ TierName) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_gradient(low = "blue", high = "yellow") +
  labs(x = "Time (rounded to the nearest hour)", y = "Percentage")

# Polar chart
ggplot(wildschwein_sum2, aes(hour, sum_rel, fill = vegetationshoehe_LFI)) +
  geom_col() +
  facet_wrap(~ TierName) +
  scale_y_continuous(labels = scales::percent) +
   scale_fill_gradient(low = "blue", high = "yellow") +
  labs(x = "Time (rounded to the nearest hour)", y = "Percentage") +
  coord_polar (start = -0.1)

```


